\documentclass{article}
\usepackage{kotex}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{scrextend}
\usepackage{setspace}
\usepackage{anyfontsize}
\geometry{a4paper, margin=1in}

\begin{document}

\renewcommand{\familydefault}{\sfdefault}
\onehalfspacing
\fontsize{12pt}{14pt}\selectfont

% Section 3
\section*{Vocabulary Words}
\begin{addmargin}[1em]{1em}
brush, test, weigh, birth, touch, tell, soft, clothes, thank, second, age, hide, lose, bath, cost, bright, puppy, ugly, pet, wish
\end{addmargin}

\section*{Vocabulary Examples}
\begin{addmargin}[1em]{1em}
\begin{itemize}
    \item The girl was \_\_\_\_\_\_ her hair before going to bed. (진행형)
    \begin{quote}
    그 소녀는 잠자리에 들기 전에 머리를 빗고 있었다.
    \end{quote}
    \item Write your name at the top of your \_\_\_\_\_\_ paper.
    \begin{quote}
    시험지 맨 위에 이름을 쓰세요.
    \end{quote}
    \item She always \_\_\_\_\_\_ herself in the morning. (3인칭 단수)
    \begin{quote}
    그녀는 항상 아침에 체중을 잰다.
    \end{quote}
    \item He was holding his baby after its \_\_\_\_\_\_.
    \begin{quote}
    그는 아기가 태어난 후 아기를 안고 있었다.
    \end{quote}
    \item \_\_\_\_\_\_ the phone to make a call.
    \begin{quote}
    전화를 걸기 위해 전화를 만지세요.
    \end{quote}
    \item The doctor was \_\_\_\_\_\_ the man about his heart. (진행형)
    \begin{quote}
    의사가 남자에게 그의 심장에 대해 말하고 있었다.
    \end{quote}
    \item She was resting on a \_\_\_\_\_\_ pillow.
    \begin{quote}
    그녀는 푹신한 베개에 기대어 쉬고 있었다.
    \end{quote}
    \item She is picking \_\_\_\_\_\_ for her trip to the beach.
    \begin{quote}
    그녀는 해변 여행을 위해 옷을 고르고 있다.
    \end{quote}
    \item Nina \_\_\_\_\_\_ her brother for the gift. (과거형)
    \begin{quote}
    니나는 선물에 대해 오빠에게 감사했다.
    \end{quote}
    \item You only have a few \_\_\_\_\_\_ to finish. (복수형)
    \begin{quote}
    끝내려면 몇 초 밖에 없다.
    \end{quote}
    \item They do a lot of activities for people of their \_\_\_\_\_\_.
    \begin{quote}
    그들은 그들의 나이에 맞는 많은 활동을 한다.
    \end{quote}
    \newpage
    \item Mark was \_\_\_\_\_\_ under the bed with his mom's computer. (진행형)
    \begin{quote}
    마크는 엄마의 컴퓨터와 함께 침대 밑에 숨고 있었다.
    \end{quote}
    \item The new car \_\_\_\_\_\_ a lot of money. (3인칭 단수)
    \begin{quote}
    새 차는 비용이 많이 든다.
    \end{quote}
    \item The dirty dog does not want to take a \_\_\_\_\_\_.
    \begin{quote}
    더러운 개는 목욕을 하고 싶어하지 않는다.
    \end{quote}
    \item Everyone agrees that Mike is a \_\_\_\_\_\_ person.
    \begin{quote}
    모두가 마이크가 똑똑하다고 동의한다.
    \end{quote}
    \item Min \_\_\_\_\_\_ her ring yesterday, but she found it today. (과거형)
    \begin{quote}
    민은 어제 반지를 잃어버렸지만 오늘 찾았다.
    \end{quote}
    \item Sleep is important for the health of a \_\_\_\_\_\_.
    \begin{quote}
    잠은 강아지의 건강에 중요하다.
    \end{quote}
    \item We saw some \_\_\_\_\_\_ birds at the zoo.
    \begin{quote}
    우리는 동물원에서 몇 마리의 못생긴 새들을 보았다.
    \end{quote}
    \item He remembered to make a \_\_\_\_\_\_ for his birthday.
    \begin{quote}
    그는 생일 소원을 비는 것을 기억했다.
    \end{quote}
    \item She thinks Rover is the best \_\_\_\_\_\_ in the world.
    \begin{quote}
    그녀는 로버가 세계 최고의 애완동물이라고 생각한다.
    \end{quote}
\end{itemize}
\end{addmargin}

\end{document}
