\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\title{English Vocabulary Quiz}
\date{}

\begin{document}

\maketitle

\section*{Fill in the blanks with the appropriate word:}

\begin{enumerate}[label=\arabic*.]

    \item Because Jane does not listen to her, Jane's mom is \_\_\_\_\_\_.
    \item Jason hates staying inside because it is so \_\_\_\_\_\_.
    \item Ryan's dad teaches a new \_\_\_\_\_\_.
    \item She \_\_\_\_\_\_ about living in the city.
    \item The kids like the \_\_\_\_\_\_ baseball player.
    \item He \_\_\_\_\_\_ very hot after walking for half the morning.
    \item In the \_\_\_\_\_\_, we will not need roads for driving.
    \item The \_\_\_\_\_\_ uses a large table to study.
    \item Her \_\_\_\_\_\_ are drawing and painting.
    \item She needs money, so she wants to get a \_\_\_\_\_\_.
    \item Five \_\_\_\_\_\_ dollars is a lot of money.
    \item Mrs. Jones \_\_\_\_\_\_ us into her home.
    \item The boy is good at \_\_\_\_\_\_.
    \item I am glad you shared these \_\_\_\_\_\_ with me.
    \item Many kids dream about becoming their country's \_\_\_\_\_\_.
    \item This TV show is \_\_\_\_\_\_ good.
    \item The woman answered a lot of questions during her \_\_\_\_\_\_.
    \item Vicky loves to \_\_\_\_\_\_. She goes to many faraway places.
    \item Janet has a beautiful \_\_\_\_\_\_. She should give singing lessons.
    \item Carlos did not bring a pencil to class today. I \_\_\_\_\_\_ why.
    \item I really like to play \_\_\_\_\_\_ with my brother.
    \item I need new shoes for playing \_\_\_\_\_\_.
    \item Going into the city alone can be \_\_\_\_\_\_.
    \item Lisa is \_\_\_\_\_\_ to hear the president's speech.
    \item I wonder what is at the top of that \_\_\_\_\_\_.
    \item Josh \_\_\_\_\_\_ the ball with his bat.
    \item The nurse at the \_\_\_\_\_\_ was nice to Janet.
    \item Max \_\_\_\_\_\_ his leg when he fell down during the game.
    \item Riding a \_\_\_\_\_\_ is one of my hobbies.
    \item The snail is a \_\_\_\_\_\_ animal.
    \item Agnes \_\_\_\_\_\_ the ball.
    \item The \_\_\_\_\_\_ here is perfect for growing things.
    \item The \_\_\_\_\_\_ shows the race is over.
    \item It was \_\_\_\_\_\_ to get close to the animal.
    \item The lady is \_\_\_\_\_\_ a bottle of water.
    \item It does not \_\_\_\_\_\_ which doctor you see. They are all good.
    \item The colorful ball is \_\_\_\_\_\_.
    \item I am going to \_\_\_\_\_\_ my little brother to a game.
    \item The game ended in a \_\_\_\_\_\_.
    \item We did not have our baseball game because of bad \_\_\_\_\_\_.
    \item One of my hobbies is making \_\_\_\_\_\_ for my parents.
    \item He dreams about \_\_\_\_\_\_ houses for a job.
    \item They are \_\_\_\_\_\_ which color they like.
    \item Martha is \_\_\_\_\_\_ a man walking with a flag.
    \item The \_\_\_\_\_\_ in the math class did not understand the lesson.
    \item In the future, she hopes to \_\_\_\_\_\_ great art for a job.
    \item These are \_\_\_\_\_\_ of my friends.
    \item There are many \_\_\_\_\_\_ on this hill.
    \item Can you please \_\_\_\_\_\_ the question?
    \item Does it matter what I put on my bedroom \_\_\_\_\_\_?
    \item Many students were \_\_\_\_\_\_ because of bad weather.
    \item The people in the \_\_\_\_\_\_ of the room could not hear.
    \item Mike had to \_\_\_\_\_\_ the window that his son broke.
    \item The \_\_\_\_\_\_ is really dry this year.
    \item Bring another pair of \_\_\_\_\_\_ with you.
    \item They are having a \_\_\_\_\_\_, and we are all invited.
    \item Hundreds of people come to surf in this \_\_\_\_\_\_ every year.
    \item Climbing \_\_\_\_\_\_ can be dangerous.
    \item We sit on the stairs in front of our \_\_\_\_\_\_.
    \item They are using \_\_\_\_\_\_ to build the house.
\end{enumerate}

\end{document}