\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\title{English Vocabulary Quiz}
\date{}

\begin{document}

\maketitle

\section*{Version A:}

\begin{enumerate}[label=\arabic*.]
    \item The nurse at the \_\_\_\_\_\_\_ was nice to Janet.
    \item Josh \_\_\_\_\_\_\_ the ball with his bat.
    \item Agnes \_\_\_\_\_\_\_ the ball.
    \item They are \_\_\_\_\_\_\_ which color they like.
    \item Riding a \_\_\_\_\_\_\_ is one of my hobbies.
    \item He \_\_\_\_\_\_\_ very hot after walking for half the morning.
    \item Many kids dream about becoming their country's \_\_\_\_\_\_\_.
    \item Mrs. Jones \_\_\_\_\_\_\_ us into her home.
    \item Vicky loves to \_\_\_\_\_\_\_. She goes to many faraway places.
    \item The people in the \_\_\_\_\_\_\_ of the room could not hear.
    \item The \_\_\_\_\_\_\_ is really dry this year.
    \item The colorful ball is \_\_\_\_\_\_\_.
    \item Because Jane does not listen to her, Jane's mom is \_\_\_\_\_\_\_.
    \item Five \_\_\_\_\_\_\_ dollars is a lot of money.
    \item This TV show is \_\_\_\_\_\_\_ good.
\end{enumerate}

\newpage

\section*{Version B:}

\begin{enumerate}[label=\arabic*.]
    \item In the \_\_\_\_\_\_\_, we will not need roads for driving.
    \item The woman answered a lot of questions during her \_\_\_\_\_\_\_.
    \item I am going to \_\_\_\_\_\_\_ my little brother to a game.
    \item Max \_\_\_\_\_\_\_ his leg when he fell down during the game.
    \item Lisa is \_\_\_\_\_\_\_ to hear the president's speech.
    \item Climbing \_\_\_\_\_\_\_ can be dangerous.
    \item They are having a \_\_\_\_\_\_\_, and we are all invited.
    \item Janet has a beautiful \_\_\_\_\_\_\_. She should give singing lessons.
    \item Jason hates staying inside because it is so \_\_\_\_\_\_\_.
    \item The kids like the \_\_\_\_\_\_\_ baseball player.
    \item Bring another pair of \_\_\_\_\_\_\_ with you.
    \item She needs money, so she wants to get a \_\_\_\_\_\_\_.
    \item Can you please \_\_\_\_\_\_\_ the question?
    \item The boy is good at \_\_\_\_\_\_\_.
    \item Ryan's dad teaches a new \_\_\_\_\_\_\_.
\end{enumerate}

\newpage

\section*{Version C:}

\begin{enumerate}[label=\arabic*.]
    \item It was \_\_\_\_\_\_\_ to get close to the animal.
    \item We did not have our baseball game because of bad \_\_\_\_\_\_\_.
    \item One of my hobbies is making \_\_\_\_\_\_\_ for my parents.
    \item The \_\_\_\_\_\_\_ shows the race is over.
    \item The \_\_\_\_\_\_\_ here is perfect for growing things.
    \item Martha is \_\_\_\_\_\_\_ a man walking with a flag.
    \item He dreams about \_\_\_\_\_\_\_ houses for a job.
    \item Many students were \_\_\_\_\_\_\_ because of bad weather.
    \item These are \_\_\_\_\_\_\_ of my friends.
    \item She \_\_\_\_\_\_\_ about living in the city.
    \item I really like to play \_\_\_\_\_\_\_ with my brother.
    \item I wonder what is at the top of that \_\_\_\_\_\_\_.
    \item Does it \_\_\_\_\_\_\_ what I put on my bedroom walls?
    \item The \_\_\_\_\_\_\_ in the math class did not understand the lesson.
    \item The group uses a large table to \_\_\_\_\_\_\_.
\end{enumerate}

\newpage

\section*{Version D:}

\begin{enumerate}[label=\arabic*.]
    \item Mike had to \_\_\_\_\_\_\_ the window that his son broke.
    \item The snail is a \_\_\_\_\_\_\_ animal.
    \item Carlos did not bring a pencil to class today. I \_\_\_\_\_\_\_ why.
    \item Hundreds of people come to surf in this \_\_\_\_\_\_\_ every year.
    \item They are using \_\_\_\_\_\_\_ to build the house.
    \item It does not \_\_\_\_\_\_\_ which doctor you see. They are all good.
    \item Riding a \_\_\_\_\_\_\_ is one of my hobbies.
    \item We sit on the stairs in front of our \_\_\_\_\_\_\_.
    \item Janet has a beautiful \_\_\_\_\_\_\_. She should give singing lessons.
    \item The \_\_\_\_\_\_\_ is really dry this year.
    \item The colorful ball is \_\_\_\_\_\_\_.
    \item Because Jane does not listen to her, Jane's mom is \_\_\_\_\_\_\_.
    \item Five \_\_\_\_\_\_\_ dollars is a lot of money.
    \item This TV show is \_\_\_\_\_\_\_ good.
    \item The kids like the \_\_\_\_\_\_\_ baseball player.
\end{enumerate}

\end{document}
