\documentclass[12pt]{article}
\usepackage{kotex}
\usepackage{geometry}
\geometry{a4paper, portrait, margin=1in}

\begin{document}

\section*{Page 1}
\begin{itemize}
    \item \textbf{angry} -- 화난 \\
    Because Jane does not listen to her, Jane's mom is \textbf{angry}.
    \item \textbf{boring} -- 지루한 \\
    Jason hates staying inside because it is so \textbf{boring}.
    \item \textbf{class} -- 수업 \\
    Ryan's dad teaches a new \textbf{class}.
    \item \textbf{dream} -- 꿈꾸다 \\
    She \textbf{dreams} about living in the city.
    \item \textbf{famous} -- 유명한 \\
    The kids like the \textbf{famous} baseball player.
    \item \textbf{feel} -- 느끼다 \\
    He \textbf{felt} very hot after walking for half the morning.
    \item \textbf{future} -- 미래 \\
    In the \textbf{future}, we will not need roads for driving.
    \item \textbf{group} -- 그룹 \\
    The \textbf{group} uses a large table to study.
    \item \textbf{hobby} -- 취미 \\
    Her \textbf{hobbies} are drawing and painting.
    \item \textbf{job} -- 직업 \\
    She needs money, so she wants to get a \textbf{job}.
    \item \textbf{hundred} -- 숫자 100 \\
    Five \textbf{hundred} dollars is a lot of money.
    \item \textbf{invite} -- 초대하다 \\
    Mrs. Jones \textbf{invited} us into her home.
    \item \textbf{math} -- 수학 \\
    The boy is good at \textbf{math}.
    \item \textbf{photograph(photo)} -- 사진 \\
    I am glad you shared these \textbf{photos} with me.
    \item \textbf{president} -- 대통령 \\
    Many kids dream about becoming their country's \textbf{president}.
\end{itemize}

\newpage
\section*{Page 2}
\begin{itemize}
    \item \textbf{really} -- 정말 \\
    This TV show is \textbf{really} good.
    \item \textbf{speech} -- 연설 \\
    The woman answered a lot of questions during her \textbf{speech}.
    \item \textbf{travel} -- 여행하다 \\
    Vicky loves to \textbf{travel}. She goes to many faraway places.
    \item \textbf{voice} -- 목소리 \\
    Janet has a beautiful \textbf{voice}. She should give singing lessons.
    \item \textbf{wonder} -- 궁금해지다 \\
    Carlos did not bring a pencil to class today. I \textbf{wonder} why.
    \item \textbf{baseball} -- 야구 \\
    I really like to play \textbf{baseball} with my brother.
    \item \textbf{basketball} -- 농구 \\
    I need new shoes for playing \textbf{basketball}.
    \item \textbf{dangerous} -- 위험한 \\
    Going into the city alone can be \textbf{dangerous}.
    \item \textbf{excited} -- 신이 난 \\
    Lisa is \textbf{excited} to hear the president's speech.
    \item \textbf{hill} -- 언덕 \\
    I \textbf{wonder} what is at the top of that \textbf{hill}.
    \item \textbf{hit} -- 치다 \\
    Josh \textbf{hit} the ball with his bat.
    \item \textbf{hospital} -- 병원 \\
    The nurse at the \textbf{hospital} was nice to Janet.
    \item \textbf{hurt} -- 다치다 \\
    Max \textbf{hurt} his leg when he fell down during the game.
    \item \textbf{motorbike} -- 오토바이 \\
    Riding a \textbf{motorbike} is one of my hobbies.
    \item \textbf{slow} -- 느린 \\
    The snail is a \textbf{slow} animal.
\end{itemize}

\newpage
\section*{Page 3}
\begin{itemize}
    \item \textbf{drop} -- 떨어뜨리다 \\
    Agnes \textbf{dropped} the ball.
    \item \textbf{earth} -- 땅 \\
    The \textbf{earth} here is perfect for growing things.
    \item \textbf{flag} -- 깃발 \\
    The \textbf{flag} shows the race is over.
    \item \textbf{foolish} -- 어리석은 \\
    It was \textbf{foolish} to get close to the animal.
    \item \textbf{hold} -- 잡다 \\
    The lady is \textbf{holding} a bottle of water.
    \item \textbf{matter} -- 문제가 되다 \\
    It does not \textbf{matter} which doctor you see. They are all good.
    \item \textbf{round} -- 둥근 \\
    The colorful ball is \textbf{round}.
    \item \textbf{take} -- 데리고 가다 \\
    I am going to \textbf{take} my little brother to a game.
    \item \textbf{tie} -- 무승부 \\
    The game ended in a \textbf{tie}.
    \item \textbf{weather} -- 날씨 \\
    We did not have our baseball game because of bad \textbf{weather}.
    \item \textbf{art} -- 미술품 \\
    One of my hobbies is making \textbf{art} for my parents.
    \item \textbf{build} -- 짓다 \\
    He dreams about \textbf{building} houses for a job.
    \item \textbf{choose} -- 고르다 \\
    They are \textbf{choosing} which color they like.
    \item \textbf{draw} -- 그리다 \\
    Martha is \textbf{drawing} a man walking with a flag.
    \item \textbf{kid} -- 아이 \\
    The \textbf{kid} in the math class did not understand the lesson.
\end{itemize}

\newpage
\section*{Page 4}
\begin{itemize}
    \item \textbf{paint} -- 그림 그리다 \\
    In the future, she hopes to \textbf{paint} great art for a job.
    \item \textbf{picture} -- 사진, 그림 \\
    These are \textbf{pictures} of my friends.
    \item \textbf{plant} -- 식물 \\
    There are many \textbf{plants} on this hill.
    \item \textbf{repeat} -- 반복하다 \\
    Can you please \textbf{repeat} the question?
    \item \textbf{wall} -- 벽 \\
    Does it matter what I put on my bedroom \textbf{walls}?
    \item \textbf{absent} -- 결석한 \\
    Many students were \textbf{absent} because of bad weather.
    \item \textbf{back} -- 뒤쪽 \\
    The people in the \textbf{back} of the room could not hear.
    \item \textbf{fix} -- 고치다 \\
    Mike had to \textbf{fix} the window that his son broke.
    \item \textbf{land} -- 땅 \\
    The \textbf{land} is really dry this year.
    \item \textbf{pants} -- 바지 \\
    Bring another pair of \textbf{pants} with you.
    \item \textbf{picnic} -- 소풍 \\
    They are having a \textbf{picnic}, and we are all invited.
    \item \textbf{river} -- 강 \\
    Hundreds of people come to surf in this \textbf{river} every year.
    \item \textbf{rock} -- 바위 \\
    Climbing \textbf{rocks} can be dangerous.
    \item \textbf{school} -- 학교 \\
    We sit on the stairs in front of our \textbf{school}.
    \item \textbf{wood} -- 나무 \\
    They are using \textbf{wood} to build the house.
\end{itemize}

\end{document}