
\documentclass{article}
\usepackage{kotex}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{scrextend}
\usepackage{setspace}
\geometry{a4paper, margin=1in}

\begin{document}

\renewcommand{\familydefault}{\sfdefault}
\onehalfspacing
\fontsize{12pt}{14pt}\selectfont

\section*{Vocabulary Examples}
\begin{addmargin}[1em]{1em}
\begin{itemize}
    \item The baby stays \_\_\_\_\_\_ to his mother.
    \item The \_\_\_\_\_\_ I am reading is about the future.
    \item There is a \_\_\_\_\_\_ girl in my art class.
    \item Will you repeat the directions to your \_\_\_\_\_\_?
    \item I like going to this \_\_\_\_\_\_ because it is not boring.
    \item For your \_\_\_\_\_\_, use soap to clean your body.
    \item Our plan is to visit a \_\_\_\_\_\_ tomorrow.
    \item The hill was both dangerous and \_\_\_\_\_\_ to climb.
    \item You should wear \_\_\_\_\_\_ when working with wood.
    \item We cannot \_\_\_\_\_\_ the animals in the mountains.
    \item We are learning about how the \_\_\_\_\_\_ works in science class.
    \item It is difficult to \_\_\_\_\_\_ the right cup.
    \item The baby uses a \_\_\_\_\_\_ to feed himself.
    \item Try to \_\_\_\_\_\_ during the weekend.
    \item \_\_\_\_\_\_ these empty bookshelves with your books.
    \item The pool is \_\_\_\_\_\_. It does not have water.
    \item What is the difference between the sun and the \_\_\_\_\_\_?
    \item I found an excellent pair of \_\_\_\_\_\_.
    \item The boy is \_\_\_\_\_\_ and ready to eat.
    \item Our house is very \_\_\_\_\_\_ and close to a beautiful lake.
\end{itemize}
\end{addmargin}
\newpage

\section*{Vocabulary Examples}
\begin{addmargin}[1em]{1em}
\begin{itemize}
    \item She is able to \_\_\_\_\_\_ the beautiful flower.
    \item This picture is an \_\_\_\_\_\_ of fine art.
    \item The angry man made a lot of \_\_\_\_\_\_.
    \item We studied the \_\_\_\_\_\_ of plants today.
    \item The group did not have its meeting at the \_\_\_\_\_\_ today.
    \item What is the \_\_\_\_\_\_ between drawing and painting a picture?
    \item The kid repeated the \_\_\_\_\_\_ answer.
    \item The broken \_\_\_\_\_\_ of glass is dangerous.
    \item The president talked about his \_\_\_\_\_\_ in the speech.
    \item Martin will be absent from school \_\_\_\_\_\_.
    \item The farm has a \_\_\_\_\_\_ where people take water to use.
    \item The river makes a loud \_\_\_\_\_\_ when it rains.
    \item She wears her \_\_\_\_\_\_ everywhere.
    \item I can see trees through the \_\_\_\_\_\_.
    \item I do not like using the \_\_\_\_\_\_ at school.
    \item Did you remember to bring water so you are not \_\_\_\_\_\_?
    \item I make a \_\_\_\_\_\_ cup of tea every morning.
    \item The weather is \_\_\_\_\_\_ today.
    \item The river is too \_\_\_\_\_\_ to swim across.
    \item One of the library \_\_\_\_\_\_ is, ``Be quiet.''
\end{itemize}
\end{addmargin}
\newpage

\section*{Vocabulary Examples}
\begin{addmargin}[1em]{1em}
\begin{itemize}
    \item We are having a picnic by the \_\_\_\_\_\_ tomorrow.
    \item He could not \_\_\_\_\_\_ how to get to the farm.
    \item There is a river by the \_\_\_\_\_\_.
    \item The grass in the yard \_\_\_\_\_\_ in the winter.
    \item We are \_\_\_\_\_\_ about a famous basketball player.
    \item I guess it will be \_\_\_\_\_\_ tomorrow.
    \item The kid used \_\_\_\_\_\_ to wash his hands.
    \item Our school visited a museum and the \_\_\_\_\_\_ this year.
    \item Use this \_\_\_\_\_\_ for your juice.
    \item The boy got \_\_\_\_\_\_ from the water.
    \item Wash that \_\_\_\_\_\_ toilet with soap and water.
    \item A lot of \_\_\_\_\_\_ live by this lake.
    \item It is too \_\_\_\_\_\_ to wear a hat today.
    \item She \_\_\_\_\_\_ for her puppy.
    \item They made a \_\_\_\_\_\_ hole into the side of the hill.
    \item Rita fixed the picture with some \_\_\_\_\_\_.
    \item I enjoy relaxing on the \_\_\_\_\_\_.
    \item It is important to be \_\_\_\_\_\_ in the library.
    \item The man ran to the \_\_\_\_\_\_ of the hill.
    \item That animal is really \_\_\_\_\_\_.
\end{itemize}
\end{addmargin}

\end{document}
