\documentclass{article}
\usepackage{kotex}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{scrextend}
\usepackage{setspace}
\usepackage{anyfontsize}
\geometry{a4paper, margin=1in}

\begin{document}

\renewcommand{\familydefault}{\sfdefault}
\onehalfspacing
\fontsize{12pt}{14pt}\selectfont

\section*{Vocabulary Words}
\begin{addmargin}[1em]{1em}
excellent, relax, example, correct, piece, museum, noise, read, library, science, glue, tomorrow, quiet, mean, book, difference, difficult, sound, guess, plan
\end{addmargin}

\section*{Vocabulary Examples}
\begin{addmargin}[1em]{1em}
\begin{itemize}
    \item We are \_\_\_\_\_\_ about a famous basketball player.
    \begin{quote}
    우리는 유명한 농구 선수에 대해 읽고 있습니다.(현재진행형으로 적어주세요)
    \end{quote}
    \item It is difficult to \_\_\_\_\_\_ the right cup.
    \begin{quote}
    올바른 컵을 추측하기 어렵습니다.
    \end{quote}
    \item Try to \_\_\_\_\_\_ during the weekend.
    \begin{quote}
    주말 동안 휴식을 취해보세요.
    \end{quote}
    \item The kid repeated the \_\_\_\_\_\_ answer.
    \begin{quote}
    그 아이는 정확한 답을 반복했습니다.
    \end{quote}
    \item That animal is really \_\_\_\_\_\_.
    \begin{quote}
    그 동물은 정말 심술궂습니다.
    \end{quote}
    \item The \_\_\_\_\_\_ I am reading is about the future.
    \begin{quote}
    내가 읽고 있는 책은 미래에 관한 것입니다.
    \end{quote}
    \item We studied the \_\_\_\_\_\_ of plants today.
    \begin{quote}
    오늘 우리는 식물 과학을 공부했습니다.
    \end{quote}
    \item The river makes a loud \_\_\_\_\_\_ when it rains.
    \begin{quote}
    비가 오면 강이 큰 소리를 냅니다.
    \end{quote}
    \item What is the \_\_\_\_\_\_ between drawing and painting a picture?
    \begin{quote}
    그림을 그리는 것과 그림을 그리는 것의 차이는 무엇입니까?
    \end{quote}
    \item I like going to this \_\_\_\_\_\_ because it is not boring.
    \begin{quote}
    이 박물관에 가는 것을 좋아합니다. 지루하지 않거든요.
    \end{quote}
    \item This picture is an \_\_\_\_\_\_ of fine art.
    \begin{quote}
    이 그림은 순수 미술의 예입니다.
    \end{quote}
    \item The weather is \_\_\_\_\_\_ today.
    \begin{quote}
    오늘 날씨가 훌륭합니다.
    \end{quote}
    \item The angry man made a lot of \_\_\_\_\_\_.
    \begin{quote}
    화난 남자가 많은 소음을 냈습니다.
    \end{quote}
    \item It is important to be \_\_\_\_\_\_ in the library.
    \begin{quote}
    도서관에서는 조용히 하는 것이 중요합니다.
    \end{quote}
    \item The group did not have its meeting at the \_\_\_\_\_\_ today.
    \begin{quote}
    그 그룹은 오늘 도서관에서 회의를 하지 않았습니다.
    \end{quote}
    \item Rita fixed the picture with some \_\_\_\_\_\_.
    \begin{quote}
    리타는 약간의 풀로 그림을 고쳤습니다.
    \end{quote}
    \item The broken \_\_\_\_\_\_ of glass is dangerous.
    \begin{quote}
    깨진 유리 조각은 위험합니다.
    \end{quote}
    \item The hill was both dangerous and \_\_\_\_\_\_ to climb.
    \begin{quote}
    그 언덕은 위험하고 오르기 어려웠습니다.
    \end{quote}
    \item Martin will be absent from school \_\_\_\_\_\_.
    \begin{quote}
    마틴은 내일 학교에 결석할 것입니다.
    \end{quote}
    \item The president talked about his \_\_\_\_\_\_ in the speech.
    \begin{quote}
    대통령은 연설에서 자신의 계획에 대해 이야기했습니다.
    \end{quote}
\end{itemize}
\end{addmargin}

\end{document}
