\documentclass{article}
\usepackage{kotex}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{scrextend}
\usepackage{setspace}
\usepackage{anyfontsize}
\geometry{a4paper, margin=1in}

\begin{document}

\renewcommand{\familydefault}{\sfdefault}
\onehalfspacing
\fontsize{12pt}{14pt}\selectfont

\section*{Vocabulary Words}
\begin{addmargin}[1em]{1em}
house, glove, mountain, soap, toilet, hat, well, top, windy, lake, moon, grass, smell, deep, close, boot, sunny, wet, wide, farm
\end{addmargin}

\section*{Vocabulary Examples}
\begin{addmargin}[1em]{1em}
\begin{itemize}
    \item It is too \_\_\_\_\_\_ to wear a hat today.
    \begin{quote}
    오늘은 바람이 너무 불어서 모자를 쓸 수 없습니다.
    \end{quote}
    \item The kid used \_\_\_\_\_\_ to wash his hands.
    \begin{quote}
    아이들은 손을 씻기 위해 비누를 사용했습니다.
    \end{quote}
    \item The man ran to the \_\_\_\_\_\_ of the hill.
    \begin{quote}
    그 남자는 언덕 꼭대기까지 달렸습니다.
    \end{quote}
    \item I guess it will be \_\_\_\_\_\_ tomorrow.
    \begin{quote}
    내일은 화창할 것 같아요.
    \end{quote}
    \item There is a river by the \_\_\_\_\_\_.
    \begin{quote}
    산 옆에 강이 있습니다.
    \end{quote}
    \item The boy got \_\_\_\_\_\_ from the water.
    \begin{quote}
    소년은 물에 젖었습니다.
    \end{quote}
    \item I found an excellent pair of \_\_\_\_\_\_.
    \begin{quote}
    나는 훌륭한 부츠 한 켤레를 찾았습니다. (복수형)
    \end{quote}
    \item She wears her \_\_\_\_\_\_ everywhere.
    \begin{quote}
    그녀는 어디든 모자를 씁니다.
    \end{quote}
    \item I do not like using the \_\_\_\_\_\_ at school.
    \begin{quote}
    나는 학교에서 변기를 사용하는 것을 좋아하지 않습니다. (복수형)
    \end{quote}
    \item She is able to \_\_\_\_\_\_ the beautiful flower.
    \begin{quote}
    그녀는 아름다운 꽃의 냄새를 맡을 수 있습니다.
    \end{quote}
    \item The farm has a \_\_\_\_\_\_ where people take water to use.
    \begin{quote}
    농장에는 사람들이 물을 사용하는 우물이 있습니다.
    \end{quote}
    \item The baby stays \_\_\_\_\_\_ to his mother.
    \begin{quote}
    아기는 엄마 가까이에 머물러 있습니다.
    \end{quote}
    \item What is the difference between the sun and the \_\_\_\_\_\_?
    \begin{quote}
    태양과 달의 차이점은 무엇입니까?
    \end{quote}
    \item I enjoy relaxing on the \_\_\_\_\_\_.
    \begin{quote}
    나는 잔디 위에서 휴식을 취하는 것을 즐깁니다.
    \end{quote}
    \item You should wear \_\_\_\_\_\_ when working with wood.
    \begin{quote}
    나무를 다룰 때는 장갑을 껴야 합니다. (복수형)
    \end{quote}
    \item Our plan is to visit a \_\_\_\_\_\_ tomorrow.
    \begin{quote}
    우리의 계획은 내일 농장을 방문하는 것입니다.
    \end{quote}
    \item The river is too \_\_\_\_\_\_ to swim across.
    \begin{quote}
    강이 너무 넓어서 건널 수 없습니다.
    \end{quote}
    \item Will you repeat the directions to your \_\_\_\_\_\_?
    \begin{quote}
    당신의 집으로 가는 길을 다시 말해주시겠습니까?
    \end{quote}
    \item We are having a picnic by the \_\_\_\_\_\_ tomorrow.
    \begin{quote}
    우리는 내일 호숫가에서 소풍을 할 것입니다.
    \end{quote}
    \item They made a \_\_\_\_\_\_ hole into the side of the hill.
    \begin{quote}
    그들은 언덕 옆에 깊은 구멍을 만들었습니다.
    \end{quote}
\end{itemize}
\end{addmargin}

\end{document}
