\documentclass{article}
\usepackage{kotex}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{scrextend}
\usepackage{setspace}
\usepackage{anyfontsize}
\geometry{a4paper, margin=1in}

\begin{document}

\renewcommand{\familydefault}{\sfdefault}
\onehalfspacing
\fontsize{12pt}{14pt}\selectfont

\section*{Vocabulary Words}
\begin{addmargin}[1em]{1em}
zoo, empty, window, thirsty, care, die, fill, large, dirty, hungry, spoon, heart, health, rule, feed, girl, glass, frog, fresh, remember
\end{addmargin}

\section*{Vocabulary Examples}
\begin{addmargin}[1em]{1em}
\begin{itemize}
    \item We cannot \_\_\_\_\_\_ the animals in the mountains.
    \begin{quote}
    우리는 산에서 동물에게 먹이를 줄 수 없습니다.
    \end{quote}
    \item \_\_\_\_\_\_ these empty bookshelves with your books.
    \begin{quote}
    이 빈 책장을 책으로 채우세요.
    \end{quote}
    \item Our house is very \_\_\_\_\_\_ and close to a beautiful lake.
    \begin{quote}
    우리 집은 매우 크고 아름다운 호수와 가깝습니다.
    \end{quote}
    \item Did you remember to bring water so you are not \_\_\_\_\_\_?
    \begin{quote}
    목이 마르지 않게 물을 가져오는 것을 기억했나요?
    \end{quote}
    \item He could not \_\_\_\_\_\_ how to get to the farm.
    \begin{quote}
    그는 농장에 가는 길을 기억할 수 없었습니다.
    \end{quote}
    \item We are learning about how the \_\_\_\_\_\_ works in science class.
    \begin{quote}
    우리는 과학 수업에서 심장이 어떻게 작동하는지 배우고 있습니다.
    \end{quote}
    \item The baby uses a \_\_\_\_\_\_ to feed himself.
    \begin{quote}
    아기는 숟가락을 사용하여 스스로 먹습니다.
    \end{quote}
    \item One of the library \_\_\_\_\_\_ is, "Be quiet."
    \begin{quote}
    도서관 규칙 중 하나는 '조용히 하라'입니다. (복수형)
    \end{quote}
    \item I can see trees through the \_\_\_\_\_\_.
    \begin{quote}
    나는 창문을 통해 나무를 볼 수 있습니다.
    \end{quote}
    \item For your \_\_\_\_\_\_, use soap to clean your body.
    \begin{quote}
    건강을 위해 비누로 몸을 씻으세요.
    \end{quote}
    \item She \_\_\_\_\_\_ for her puppy. (3인칭 동사형)
    \begin{quote}
    그녀는 강아지를 보살핍니다.
    \end{quote}
    \newpage
    \item A lot of \_\_\_\_\_\_ live by this lake.
    \begin{quote}
    이 호수에는 많은 개구리들이 삽니다.(복수형)
    \end{quote}
    \item The grass in the yard \_\_\_\_\_\_ in the winter.
    \begin{quote}
    겨울에 마당의 잔디가 죽었습니다. (과거형)
    \end{quote}
    \item The boy is \_\_\_\_\_\_ and ready to eat.
    \begin{quote}
    소년은 배가 고파서 먹을 준비가 되어 있습니다.
    \end{quote}
    \item Use this \_\_\_\_\_\_ for your juice.
    \begin{quote}
    이 유리컵을 주스로 사용하세요.
    \end{quote}
    \item Wash that \_\_\_\_\_\_ toilet with soap and water.
    \begin{quote}
    그 더러운 변기를 비누와 물로 씻으세요.
    \end{quote}
    \item Our school visited a museum and the \_\_\_\_\_\_ this year.
    \begin{quote}
    우리 학교는 올해 박물관과 동물원을 방문했습니다.
    \end{quote}
    \item The pool is \_\_\_\_\_\_. It does not have water.
    \begin{quote}
    수영장이 비어 있습니다. 물이 없습니다.
    \end{quote}
    \item I make a \_\_\_\_\_\_ cup of tea every morning.
    \begin{quote}
    나는 매일 아침 신선한 차를 한 잔 만듭니다.
    \end{quote}
    \item There is a mean \_\_\_\_\_\_ in my art class.
    \begin{quote}
    내 미술 수업에 심술궂은 소녀가 있습니다.
    \end{quote}
\end{itemize}
\end{addmargin}

\end{document}
