\documentclass{article}
\usepackage{kotex}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{scrextend}
\usepackage{setspace}
\geometry{a4paper, margin=1in}

\begin{document}

\renewcommand{\familydefault}{\sfdefault}
\onehalfspacing

% Page 1
\section*{Vocabulary List}
\begin{addmargin}[1em]{1em}
    \begin{itemize}
        \item \fontsize{12pt}{14pt}\selectfont \textbf{book} - 책 \newline
        The \textbf{book} I am reading is about the future. \newline
        내가 읽고 있는 책은 미래에 관한 것입니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{example} - 예 \newline
        This picture is an \textbf{example} of fine art. \newline
        이 그림은 순수 미술의 예입니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{glue} - 풀 \newline
        Rita fixed the picture with some \textbf{glue}. \newline
        리타는 약간의 풀로 그림을 고쳤습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{library} - 도서관 \newline
        The group did not have its meeting at the \textbf{library} today. \newline
        그 그룹은 오늘 도서관에서 회의를 하지 않았습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{mean} - 심술궂은 \newline
        That animal is really \textbf{mean}. \newline
        그 동물은 정말 심술궂습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{piece} - 조각 \newline
        The broken \textbf{piece} of glass is dangerous. \newline
        깨진 유리 조각은 위험합니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{plan} - 계획 \newline
        The president talked about his \textbf{plan} in the speech. \newline
        대통령은 연설에서 자신의 계획에 대해 이야기했습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{quiet} - 조용한 \newline
        It is important to be \textbf{quiet} in the library. \newline
        도서관에서는 조용히 하는 것이 중요합니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{read} - 읽다 \newline
        We are \textbf{reading} about a famous basketball player. \newline
        우리는 유명한 농구 선수에 대해 읽고 있습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{sound} - 소리 \newline
        The river makes a loud \textbf{sound} when it rains. \newline
        비가 오면 강이 큰 소리를 냅니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{correct} - 정확한 \newline
        The kid repeated the \textbf{correct} answer. \newline
        그 아이는 정확한 답을 반복했습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{difference} - 차이 \newline
        What is the \textbf{difference} between drawing and painting a picture? \newline
        그림을 그리는 것과 그림을 그리는 것의 차이는 무엇입니까?
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{difficult} - 어려운 \newline
        The hill was both dangerous and \textbf{difficult} to climb. \newline
        그 언덕은 위험하고 오르기 어려웠습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{excellent} - 훌륭한 \newline
        The weather is \textbf{excellent} today. \newline
        오늘 날씨가 훌륭합니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{guess} - 추측하다 \newline
        It is difficult to \textbf{guess} the right cup. \newline
        올바른 컵을 추측하기 어렵습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{museum} - 박물관 \newline
        I like going to this \textbf{museum} because it is not boring. \newline
        이 박물관에 가는 것을 좋아합니다. 지루하지 않거든요.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{noise} - 소음 \newline
        The angry man made a lot of \textbf{noise}. \newline
        화난 남자가 많은 소음을 냈습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{relax} - 휴식을 취하다 \newline
        Try to \textbf{relax} during the weekend. \newline
        주말 동안 휴식을 취해보세요.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{science} - 과학 \newline
        We studied the \textbf{science} of plants today. \newline
        오늘 우리는 식물 과학을 공부했습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{tomorrow} - 내일 \newline
        Martin will be absent from school \textbf{tomorrow}. \newline
        마틴은 내일 학교에 결석할 것입니다.
    \end{itemize}
\end{addmargin}

\newpage

% Page 2
\section*{Vocabulary List (Continued)}
\begin{addmargin}[1em]{1em}
    \begin{itemize}
        \item \fontsize{12pt}{14pt}\selectfont \textbf{close} - 가까운 \newline
        The baby stays \textbf{close} to his mother. \newline
        아기는 엄마 가까이에 머물러 있습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{grass} - 잔디 \newline
        I enjoy relaxing on the \textbf{grass}. \newline
        나는 잔디 위에서 휴식을 취하는 것을 즐깁니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{hat} - 모자 \newline
        She wears her \textbf{hat} everywhere. \newline
        그녀는 어디든 모자를 씁니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{lake} - 호수 \newline
        We are having a picnic by the \textbf{lake} tomorrow. \newline
        우리는 내일 호숫가에서 소풍을 할 것입니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{moon} - 달 \newline
        What is the difference between the sun and the \textbf{moon}? \newline
        태양과 달의 차이점은 무엇입니까?
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{mountain} - 산 \newline
        There is a river by the \textbf{mountain}. \newline
        산 옆에 강이 있습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{smell} - 냄새맡다 \newline
        She is able to \textbf{smell} the beautiful flower. \newline
        그녀는 아름다운 꽃의 냄새를 맡을 수 있습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{soap} - 비누 \newline
        The kid used \textbf{soap} to wash his hands. \newline
        아이들은 손을 씻기 위해 비누를 사용했습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{toilet} - 변기 \newline
        I do not like using the \textbf{toilets} at school. \newline
        나는 학교에서 변기를 사용하는 것을 좋아하지 않습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{wet} - 젖은 \newline
        The boy got \textbf{wet} from the water. \newline
        소년은 물에 젖었습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{boot} - 부츠 \newline
        I found an excellent pair of \textbf{boots}. \newline
        나는 훌륭한 부츠 한 켤레를 찾았습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{deep} - 깊은 \newline
        They made a \textbf{deep} hole into the side of the hill. \newline
        그들은 언덕 옆에 깊은 구멍을 만들었습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{farm} - 농장 \newline
        Our plan is to visit a \textbf{farm} tomorrow. \newline
        우리의 계획은 내일 농장을 방문하는 것입니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{glove} - 장갑 \newline
        You should wear \textbf{gloves} when working with wood. \newline
        나무를 다룰 때는 장갑을 껴야 합니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{house} - 집 \newline
        Will you repeat the directions to your \textbf{house}? \newline
        당신의 집으로 가는 길을 다시 말해주시겠습니까?
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{sunny} - 화창한 \newline
        I guess it will be \textbf{sunny} tomorrow. \newline
        내일은 화창할 것 같아요.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{top} - 꼭대기 \newline
        The man ran to the \textbf{top} of the hill. \newline
        그 남자는 언덕 꼭대기까지 달렸습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{well} - 우물 \newline
        The farm has a \textbf{well} where people take water to use. \newline
        농장에는 사람들이 물을 사용하는 우물이 있습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{wide} - 넓은 \newline
        The river is too \textbf{wide} to swim across. \newline
        강이 너무 넓어서 건널 수 없습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{windy} - 바람이 부는 \newline
        It is too \textbf{windy} to wear a hat today. \newline
        오늘은 바람이 너무 불어서 모자를 쓸 수 없습니다.
    \end{itemize}
\end{addmargin}

\newpage

% Page 3
\section*{Vocabulary List (Continued)}
\begin{addmargin}[1em]{1em}
    \begin{itemize}
        \item \fontsize{12pt}{14pt}\selectfont \textbf{care} - 보살피다 \newline
        She \textbf{cares} for her puppy. \newline
        그녀는 강아지를 보살핍니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{die} - 죽다 \newline
        The grass in the yard \textbf{died} in the winter. \newline
        겨울에 마당의 잔디가 죽었습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{empty} - 비어 있는 \newline
        The pool is \textbf{empty}. It does not have water. \newline
        수영장이 비어 있습니다. 물이 없습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{feed} - 먹이를 주다 \newline
        We cannot \textbf{feed} the animals in the mountains. \newline
        산에서 동물에게 먹이를 줄 수 없습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{health} - 건강 \newline
        For your \textbf{health}, use soap to clean your body. \newline
        건강을 위해 비누로 몸을 씻으세요.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{heart} - 심장 \newline
        We are learning about how the \textbf{heart} works in science class. \newline
        우리는 과학 수업에서 심장이 어떻게 작동하는지 배우고 있습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{large} - 큰 \newline
        Our house is very \textbf{large} and close to a beautiful lake. \newline
        우리 집은 매우 크고 아름다운 호수와 가깝습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{remember} - 기억하다 \newline
        He could not \textbf{remember} how to get to the farm. \newline
        그는 농장에 가는 길을 기억할 수 없었습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{rule} - 규칙 \newline
        One of the library \textbf{rules} is, "Be quiet." \newline
        도서관 규칙 중 하나는 '조용히 하라'입니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{zoo} - 동물원 \newline
        Our school visited a museum and the \textbf{zoo} this year. \newline
        우리 학교는 올해 박물관과 동물원을 방문했습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{dirty} - 더러운 \newline
        Wash that \textbf{dirty} toilet with soap and water. \newline
        그 더러운 변기를 비누와 물로 씻으세요.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{fill} - 채우다 \newline
        \textbf{Fill} these empty bookshelves with your books. \newline
        이 빈 책장을 책으로 채우세요.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{fresh} - 신선한 \newline
        I make a \textbf{fresh} cup of tea every morning. \newline
        나는 매일 아침 신선한 차를 한 잔 만듭니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{frog} - 개구리 \newline
        A lot of \textbf{frogs} live by this lake. \newline
        이 호수에는 많은 개구리들이 삽니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{girl} - 소녀 \newline
        There is a \textbf{mean} \textbf{girl} in my art class. \newline
        내 미술 수업에 심술궂은 소녀가 있습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{glass} - 유리컵 \newline
        Use this \textbf{glass} for your juice. \newline
        이 유리컵을 주스로 사용하세요.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{hungry} - 배고픈 \newline
        The boy is \textbf{hungry} and ready to eat. \newline
        소년은 배가 고파서 먹을 준비가 되어 있습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{spoon} - 숟가락 \newline
        The baby uses a \textbf{spoon} to feed himself. \newline
        아기는 숟가락을 사용하여 스스로 먹습니다.
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{thirsty} - 목마른 \newline
        Did you remember to bring water so you are not \textbf{thirsty}? \newline
        목이 마르지 않게 물을 가져오는 것을 기억했나요?
        
        \item \fontsize{12pt}{14pt}\selectfont \textbf{window} - 창문 \newline
        I can see trees through the \textbf{window}. \newline
        나는 창문을 통해 나무를 볼 수 있습니다.
    \end{itemize}
\end{addmargin}

\end{document}
